\documentclass[10pt, a4paper]{moderncv}

\usepackage[scale=0.85]{geometry}
\usepackage{tcolorbox}
\usepackage[T1]{fontenc}
\usepackage[sfdefault,light,medium]{josefin}
\usepackage{enumitem}

\moderncvstyle{classic}
\moderncvcolor{blue}

\name{Rodrigo}{Maganha Stramantinoli}

\email{rodrigostramantinoli@gmail.com}
\social[linkedin]{rodrigo-maganha}
\social[github]{ropoko}

\begin{document}
\makecvtitle

Tech and open source enthusiast.

\vspace{10pt}

\section{Work Experience}

\cventry{May 2023 -- Present}{Full Stack Developer}{Fetchly}{Remote}{}{
  Currently working with a wide-variety of projects with different technologies, like Ruby, Python, Typescript, React and Vue.
}

\cventry{Oct. 2022 -- Mar. 2023}{Frontend Developer}{Compass UOL}{Remote}{}{
Worked on my first international project, focused in accessibility for blind people, had to dive deep into HTML semantics and how screen readers app do things.
The project is n e-commerce, built React and Oracle Cloud Commerce for defining the overall commerce structure.
}

\cventry{May 2021 -- Apr. 2022}{Full Stack Developer}{Zella - Sistemas Inteligentes}{Barra Bonita -- SP}{}{
Helped creating a culture in the company, defining some basic gitflow and general configuration related to CI/CD.
Also started building an Angular + .NET ecosystem, creating internal libraries and tools.
\newline{}
The most expressive project in the company was a real time web app using mqtt + raspberry pi for a logistics automation project.
}

\cventry{Jan. 2020 -- Dec. 2020}{Intern Developer}{Zella - Sistemas Inteligentes}{Barra Bonita -- SP}{}{
Mostly studying C\# and the web basics (JavaScript) and Desktop using Windows Forms.
Helped building internal tools for the company.
}

\cventry{2018}{Startup Google -- Regional Highlight}{}{}{}{
We built a prototype to show events and shows in the region, the idea was to give the users a list where they could confirm presence and have a list to see all the next shows.
\newline{}
Our team got the regional highlight achievement developing a prototype with the proposed theme.
}

\cventry{2018}{Volunteer Work}{Barra Bonita -- SP}{}{}{
Helped volunteers on a scholar project, helping elderly people starting using the internet and how to use the basics of the Office Package (Word, PowerPoint, …)
}

% EDUCATION
\section{Education}

\cventry{2021 -- 2025}{Computer Science}{Unisagrado}{Bauru -- SP}{}{
Studying the fundamentals of Computer Science.
}

\cventry{2017 -- 2020}{Technical High School}{ETEC Comendador João Rays}{Barra Bonita -- SP}{}{
Technical High School with initial programming and logic learning.
}

% PROJECTS
\section{Open Source Projects}

\cventry{}{Wild League -- Gaming on Fediverse}{}{}{}{Personal project implementing the ActivityPub protocol for a "tower defense" card game in real time, integrated into the fediverse.}

\cventry{}{Vivaldi Browser -- Translator}{}{}{}{Voluntary translation of the Vivaldi browser from English to Brazilian Portuguese.}

\cventry{}{CLI Dictionary}{\href{https://github.com/cli-dictionary/cli-dictionary}{github.com/cli-dictionary/cli-dictionary}}{}{}{Command line dictionary in Python, available on Snapcraft with about 200 users and support for 13 languages.}

\section{Interesses}

\vspace{8pt}

\begin{itemize}[leftmargin=4cm]
  \item Music
  \item Linux
  \item Game Development
\end{itemize}

\end{document}
